### 2018-11-28 chapters/3-results.tex
readability

The prediction performance of the models trained using regularized logistic
regression was estimated by LPOCV\@. Table~\ref{tab:auc_imagetype} contains the
results for models within each image type using all or top 1\% of the features.
The results are AUC values with confidence intervals included.

@@

In contrast, logistic regression utilizing L2 regularization showed better
performance than using L1 regularization for all image types except for T₂w
where AUC dropped to 0.68, DWI derived parametric maps (ADCₘ, ADCₖ, K) had AUC
between 0.69 to 0.73, and T₂ derived features had AUC=0.70.

These results indicate that an L2 regularized logistic regression model with
all features might perform better than a logistic regression model with fewer
features selected by L1 regularization for all image types except T₂w. However,
it should be noticed that with T₂w L1 regularization performed better than L2,
suggesting that a subset of features would performed better than all of them.

>>>>

The prediction performance of the models trained using regularized logistic
regression was estimated by LPOCV\@. Both L1 and L2 regularization methods were
utilized separately. Table~\ref{tab:auc_imagetype} contains the results for
models within each image type using all or top 1\% of the features. The results
are AUC values with confidence intervals included.

@@

In contrast to L1, L2 regularization yielded better performance for all image
types except for T₂w where AUC dropped to 0.68. DWI derived parametric maps
(ADCₘ, ADCₖ, K) had AUC between 0.69 to 0.73, and T₂ derived features had
AUC=0.70.

These results indicate that, when it comes to logistic regression models, L2
regularization with all features may perform better than fewer features
selected by L1, for all of the image types except T₂w. With T₂w,
L1 regularization performed better than L2, suggesting that a subset of
features would perform better than all of them.
